trialStreaks

### 2018-09-06 E1/trialStreaksE1.Rmd
good

```{r}
lr<- lr %>% mutate(orientCI = ifelse(orientation=="Canonical",1,-1))

@@

>>>>

```{r}
lr <- lr %>% filter(excludeOrNot==FALSE)
lr<- lr %>% mutate(orientCI = ifelse(orientation=="Canonical",1,-1))

@@

Use stat_summary to average across Ss in plot

```{r , fig.height=5, fig.width=5}
lr_autocorr %>% 
    ggplot(aes(x = lag, y = cor)) +
    # Add horizontal line a y=0
    geom_hline(yintercept = 0) +
    # Plot autocorrelations
stat_summary(fun.y="mean",geom="point",size=4) + 
  ggtitle('after exclusions') + 
  stat_summary(fun.data = mean_cl_boot, geom="errorbar", width=0.4) +
    # Add facets
    #facet_wrap(~ subject, ncol = 3) +
    # Aesthetics
    expand_limits(y = c(-.1, .1)) +
    #scale_color_tq() +
    stat_summary(fun.y="mean",geom="line") + #,aes(group=orientation))
    theme_tq() +
    xlab("Lag") + ylab('Correlation of leftBias with orientation of trial lag in past')
    theme(
        legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1)
    )
```
